\chapter{Crowdfunding} % (fold)
\label{cha:crowdfunding}

The Legacy project will be funded through a token crowdsale. The Legacy token, called LEG, serves two main purposes: it is used internally to execute the smart contracts residing in the Ethereum blockchain; and it allows for profit sharing among its holders.  Appendix \ref{} The token sale process follows standard modalities established in the blockchain ecosystem. In addition, it is in the Legacy spirit to provide additional investor protection by following recent recommendations given by the community. In particular, a minimum cap (or soft cap) target has been established, meaning that investor’s contributions will be refunded in case this target is not reached. Table \ref{table:ico_summary} summarizes the main aspects of the crowdsale.

\begin{table}[h]
	\begin{center}
		% \resizebox{\columnwidth}{!}
		% {
			\small
			\begin{tabular}{| l | p{5cm} | p{3cm}  |}	
		    \hline	
		    %\textbf{RA scheme} 	& \textbf{Peak  $T_{max}$ [b/s/Hz]}	& 	\textbf{$T$ at target $P_e\leq10^{-3}$ [b/s/Hz]}  &  \textbf{Observations}  \\ \hline    
		    	Total Supply		&  100 000 000 [LEG]  \\ \hline
		    	Auction Model       &  Ascending-price auction \\ \hline
				Starting date       &  2017/09/15\footnote{Not confirmed.} \\ \hline
				Ending date         &  starting date + 4 weeks or when the max cap is reached \\ \hline
				Maximum cap         &  100 000 [ETH] \\ \hline
				Soft cap            &  10 000 [ETH] \\ \hline
				Percentage of supply available for investors & 75\% \\ \hline
				Percentage of supply for Legacy founders     &  6\% \\ \hline
				Percentage of supply for Legacy Organization & 15\% \\ \hline
				Percentage of supply for advisors, partners and consultants & 4\% \\
			\hline	
			\end{tabular}				
		% }
	\caption{Token sale summary.}
	\label{table:ico_summary}		
	\end{center}
\end{table}


LEG tokens will be created dynamically during the token sale period. Once this period is finished, no additional tokens will be generated. A maximum of 100.000.000 LEG will be created. The token sale period finishes automatically at the predefined ending date or when the maximum cap is reached, whichever comes first.

The token sale follows a linear ascending-price model, according to Table \ref{table:ico_summary}.

\begin{table}[h]
	\begin{center}
		% \resizebox{\columnwidth}{!}
		% {
			\small
			\begin{tabular}{| l | p{5cm} | p{3cm}  |}	
		    \hline	
		    %\textbf{RA scheme} 	& \textbf{Peak  $T_{max}$ [b/s/Hz]}	& 	\textbf{$T$ at target $P_e\leq10^{-3}$ [b/s/Hz]}  &  \textbf{Observations}  \\ \hline    
		    	Phase I		&  1 ETH = 1000 LEG  \\ \hline
		    	Phase II		&  1 ETH = 900 LEG  \\ \hline
		    	Phase III	&  1 ETH = 800 LEG  \\ \hline
		    	Phase IV		&  1 ETH = 700 LEG  \\		    	
			\hline	
			\end{tabular}				
		% }
	\caption{Token price.}
	\label{table:ico_summary}		
	\end{center}
\end{table}

Detailed instructions for contributing to the crowdfunding campaign will be published on the official Legacy website several days before the starting date.  
Crowdsale Objectives

% Include diagram showing functionalities vs level of funding reached.
% What can we provide with minimum fund? with 2x min fund? with maximum fund?

% chapter crowdfunding (end)


