\chapter{The Team} % (fold)
\label{cha:the_team}

As shown throughout this paper, the Legacy Project involves several technical challenges. 
Legacy will not be an easy task, creating it will take time and will require a strong team capable of developing a product that will be used by our customers.

The Legacy team is composed by entrepreneurs and engineers with proven track records in creating, running and managing startup companies. Most of them participated in startup accelerator programs and founded companies which have delivered valuable products.

\vspace{5mm} 
 
\noindent
\textbf{Felipe Faraggi} \\
\textbf{CEO} \\
linkedin \\
Solidity Documentation Translator / Entrepreneur / Python Developer \\
Previous projects: etheresante.com, willty.com, yagan.io, lavillenue.fr \\
Master in Urban Architecture, Universidad Diego Portales, Santiago, Chile

\vspace{5mm} %5mm vertical space
 
\noindent
\textbf{Vicente Almonacid} \\
\textbf{R\&D} \\
linkedin \\
PhD Candidate / Network \& Communications Protocols / Satellite and IoT/M2M \\
MEng. TELECOM Bretagne, Brest, France; BSc in Telematics Engineering, USM, Valparaíso, Chile.

\vspace{5mm} %5mm vertical space
 
\noindent
\textbf{Guillaume Figielski} \\
\textbf{Architecture} \\
linkedin \\
CS Engineer / Solidity Specialist / VR Professional \\
Previous projects: girosense.com \\
French Engineer in Computer Science, 3IL (Engineer school), Limoges, France. \\
MS in Software Engineering, University of Quebec at Chicoutimi (UQAC), Chicoutimi, Canada. \\

\vspace{5mm} %5mm vertical space
 
\noindent
\textbf{Nicolas Michel} \\
\textbf{System Operations} \\
linkedin \\
CS Engineer / Blockchain Specialist / Legal Theory \\
Previous projects: unooc.fr, axonaut.com \\
MS in Software Engineering, University of Toulouse (Paul Sabatier), Toulouse, France. \\

\vspace{5mm} %5mm vertical space
 
\noindent 
\textbf{Nicolas Ricard} \\
\textbf{Lead Developer}  \\
linkedin \\
CS Engineer / Web developer / Backend \\
Previous projects: unooc.fr, axonaut.com \\
MS in Software Engineering, University of Toulouse (Paul Sabatier), Toulouse, France. \\

\section{Transparency} % (fold)
\label{sec:transparency}
Ensuring transparent communication with the community is one of the top priorities of Legacy. The team is committed to actively provide updates and to quickly respond to feedback from investors, token holders and users.

Official communication channels will be listed on Legacy’s website.

KPI reports, as well as more detailed analysis will be periodically published on our website and transmitted to the mailing list.

% section transparency (end)

% chapter the_team (end)